Tall

### 2022-07-22 graphs_newt_snakes/Tall_GA1.Rmd
thinking about what an allele is in slim

plotty_mean_min<-plotty_mean
plotty_mean_min_s<-plotty_mean_min[which(plotty_mean_min$species=="snake"),]
plotty_mean_min_s$newt_values<-plotty_mean_min[which(plotty_mean_min$species=="newt"),"measurement"]
plotty_mean_min_s$edge <- "FALSE"
#plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(0, 1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20, 39, 40, 59, 60, 79, 80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98,99)

plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(1,2,3,5, 9,10, 14,15, 19,20, 24,25, 29,30, 34,35, 39,40, 44,45, 49,50, 54,55, 59,60, 64,65, 69,70, 74,75, 79,80, 84,85, 89,90, 94, 96, 97,98)

plotty_mean_min_s$info[plotty_mean_min_s$edge=="TRUE"]  <- "edge"
plotty_mean_min_s$info[plotty_mean_min_s$edge=="FALSE"]  <- "middle"
#plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 19, 80, 99)] <- "corner"
plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 4, 95, 99)] <- "corner"
p <- plotty_mean_min_s %>%
  plot_ly(
    x = ~as.numeric(newt_values), 
    y = ~as.numeric(measurement), 
    frame = ~generation, 
    text = ~factor(location), 
    color = ~factor(info), 
    hoverinfo = "text",
    type = 'scatter',
    mode = 'markers'
  ) %>%
  layout(
    xaxis = list(
      type = "log"
    )
  )
p
```

>>>>

plotty_mean_min<-plotty_mean
plotty_mean_min_s<-plotty_mean_min[which(plotty_mean_min$species=="snake"),]
plotty_mean_min_s$newt_values<-plotty_mean_min[which(plotty_mean_min$species=="newt"),"measurement"]
#plotty_mean_min_s$edge <- "FALSE"
#plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(0, 1, 2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20, 39, 40, 59, 60, 79, 80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98,99)

#plotty_mean_min_s$edge <- plotty_mean_min_s$location %in% list(1,2,3,5, 9,10, 14,15, 19,20, 24,25, 29,30, 34,35, 39,40, 44,45, 49,50, 54,55, 59,60, 64,65, 69,70, 74,75, 79,80, 84,85, 89,90, 94, 96, 97,98)

#plotty_mean_min_s$info[plotty_mean_min_s$edge=="TRUE"]  <- "edge"
#plotty_mean_min_s$info[plotty_mean_min_s$edge=="FALSE"]  <- "middle"
plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(0, 19, 80, 99)] <- "corner"
plotty_mean_min_s$info[plotty_mean_min_s$location %in% list(1,2,3,5, 9,10, 14,15, 19,20, 24,25, 29,30, 34,35, 39,40, 44,45, 49,50, 54,55, 59,60, 64,65, 69,70, 74,75, 79,80, 84,85, 89,90, 94, 96, 97,98)] <- "edge"
plotty_mean_min_s$info[is.na(plotty_mean_min_s$info)]<- "middle"
#unique(plotty_mean_min_s$info)
p <- plotty_mean_min_s %>%
  plot_ly(
    x = ~as.numeric(newt_values), # newt pheno
    y = ~as.numeric(measurement), #snake pheno
    frame = ~generation, 
    text = ~factor(location), 
    color = ~info, 
    hoverinfo = "text",
    type = 'scatter',
    mode = 'markers'
  ) %>%
  layout(
    xaxis = list(
      type = "log"
    )
  )
p
```
